\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-05-09 main.tex
Major update, fixing most todos

\paragraph{Internet origins at stake}
The different trust domains
correspond to different Internet origins. A major goal for web
application security is preventing undesired communication across
origins. 
%
With the goal of separating information from the different origins,
today's browsers enforce the \emph{same-origin policy} (SOP). SOP
only allows access between two documents if they share the
origin. In addition, a document can only directly communicate with the
server from which it originates. 
\todo{More?} Typically a document is considered to be an HTML-page.

@@

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.

\todo{Describe general scenario with forward pointer}
We present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

\paragraph{Evaluation and mitigation}
We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web
sites. 
%
Unfortunately, several major web sites do not protect against polyglot
attacks. Five out of the top 100 Alexa web sites are vulnerable to syntax injection
attacks. In addition,
we have found two major 
enterprise cloud storage services to be susceptible to content
smuggling attacks.
%
Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (such as PDF readers) show how to mitigate the attacks.

@@

This section describes how formats can be crossed and how that can be abused 
to cross origins by circumventing the same-origin policy. We begin by 
generalizing the problem of crossing formats to \emph{polyglots} and then describe the  
characteristics of a malicious polyglot. From that we derive two attack vectors and 
show how previous work on the subject relate to these vectors.

@@

Other examples of problematic elements include the \emph{object} and
\emph{embed} tags. These 
tags allow inclusion of resources that may require a 
plug-in to run. The plug-in is selected based on the MIME-type of the content, but
because the server delivering the content might not be able to determine its
format, the tags allow a developer to set the type-attribute to guide the
browser in which plug-in to run. When the type attribute is used, the
corresponding plug-in is run regardless of the MIME-type provided by the server. 
%
In the event that the provided MIME-type do not match that for which the plug-in is 
designed, e.g., \emph{text/html} for a PDF plug-in, it is up to the plug-in to respond to the content it is served.
Known methods of handling MIME-types, such as content-sniffing, are effective 
in this situation, but they have to be employed by each and every plug-in.
Most plug-ins will disregard the MIME-type of the content and attempt to parse 
it. 
%

As with images, the content handled by the plug-in is executed in the origin it was served from. 
This implies that the containing page is restricted 
from directly accessing the content handled by the plug-in, and that the content can 
communicate freely with the origin it was loaded from. However,  a number of plug-ins provide 
an API for interaction between the plug-in and the document.
The browsers are forced to rely on the plug-ins to employ correct security 
measures. Section~\ref{sec:eval} shows that even state-of-the-art plug-ins fail to properly do so. As we will show, this can lead to 
to cross-origin information leaks.

@@

Barth et al.~\cite{Barth+:SP09} define \emph{chameleon} documents, 
in which a benign file type crossbred with malicious HTML content. The document 
is crafted in such a way that the content-sniffing algorithm used in the browser 
will detect the content type as HTML. The paper proceeds to 
describe how an attacker can create a 
\emph{chameleon} document, that is valid PostScript, but will be identified as HTML.
This issue allows exploitation when there is a mismatch between a websites 
content validation filter and the browsers content-sniffing algorithm.

In literature we find, apart from chameleons, other names for similar,
related concepts. Brandis~\cite{Brandis:GIFAR} refer to \emph{GIFAR} 
attacks, based on one of the early instances of attacks based on 
GIF/JAR polyglots. 
Sundareswaran et al.~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10}
discuss GIFAR-related attacks as a form of \emph{content repurposing} attack. 
In this paper the term content smuggling is used as it best represents 
how a polyglot can infiltrate an origin.

@@

\subsection{Attack vectors}
\label{sec:vectors}
%In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more %than one way.
This paper identifies two vectors for infiltrating an origin, either via syntax 
injection, or content smuggling. In the case of syntax injection, existing content is manipulated
to become a polyglot, whereas with content smuggling, a polyglot is used to evade 
content filters.

\subsubsection{Syntax injection}
\label{sec:injection}
In a cross-site scripting attack user input is used to compose an HTML document. 
Fragments of HTML-syntax in the input alters the semantic of the document to 
execute attacker supplied 
script code. Similarly, in a syntax injection attack the vulnerable target will 
compose content from attacker controlled input containing syntax of a foreign 
format, thereby creating a polyglot. The polyglot is benign when viewed as the 
original format, but malicious when viewed as the injected format. While the 
targeted service serves the content as its original format, it is in the hands 
of the attacker to decide how it is interpreted. Examples of 
such services include social networks, search engines, i.e., nearly any dynamic user driven website.
%
The targeted service is assumed to employ server-side cross-site scripting 
sanitization. Hence, for the attack to be successful, the input must 
bypass this sanitization. The sanitization filter will remove or encode 
problematic characters related to HTML-syntax, based on the context of the web application. In a polyglot attack
the injected format will pose as a new context, unknown to the filter. Chances are that the 
key elements of the injected format will pass the filter unaltered.

@@

\paragraph{Scenario}
The scenario, illustrated in Figure~\ref{fig:injection-scenario}, describes how 
the attack proceeds from the infiltration of the origin to the compromise of the victim.
The victim in this scenario is an authenticated user of the targeted website, \emph{vulnerable.com}. 
The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
At a certain point, while still authenticated to \emph{vulnerable.com}, 
the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com} (1).
The \emph{attacker.com} site serves a page that embeds the content from \emph{vulnerable.com} (2). 
The attacker supplies polyglot syntax in the input to the vulnerable 
service, e.g. in the parameters of the request for the embedded content (3).
The \emph{vulnerable.com} service responds with content of the benign content type (4), but
the way it is embedded in the attackers page coerces the browser to interpret it as the malicious content type.
The malicious payload is executed in the origin of \emph{vulnerable.com} and can 
hence leverage the credentials of the victim to further exploit the vulnerability.

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{injection-scenario.png}
  \caption{Overview of the syntax injection scenario}
  \label{fig:injection-scenario}
\end{figure}

@@

\subsubsection{Content smuggling}
\label{sec:smuggling}
The vulnerable target of a content smuggling attack, lets 
users submit files to the service which are subsequently served under the origin of 
the service. Examples of such potentially vulnerable services are cloud storage services, image databases, 
social networks, conference management systems or job broker services. Such a service 
accepts a limited set of file-formats, and the files are run through a filter to verify that they 
belong to this set, e.g. images, before being served to the end
user. The
service will verify the file under the assumption that it conforms strictly to one format. 
By submitting a polyglot to such a service, an attacker can evade the filter as the polyglot does conform to the benign format.
Since the attacker can coerce the content to be interpreted as the malicious format, the
service is tricked into serving malicious content.

@@

\paragraph{Scenario}
The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:smuggling-scenario}.
The victim in this scenario is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
The target is infiltrated by the attacker (1), manipulating the website to
serve polyglot content. 
The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
At a certain point, while still authenticated to \emph{vulnerable.com}, 
the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com} (2).
The \emph{attacker.com} site embeds the polyglot content from \emph{vulnerable.com} (3), but
coerces the browser to interpret it as the malicious content type (4). 
The capabilities of the malicious format determine the 
severity of the consequences of exploitation (5).

To give more context to the scenario, \emph{vulnerable.com} can be a cloud storage service. 
The attacker infiltrates the target by uploading a polyglot to the service and embedding it 
on \emph{attacker.com}. While authenticated to \emph{vulnerable.com}, the unsuspecting victim visits \emph{attacker.com}, the embedded 
polyglot is activated and extracts all the files stored in the victims account.

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
  \caption{Overview of the content smuggling scenario}
  \label{fig:smuggling-scenario}
\end{figure}

\subsection{Payloads}
\label{sec:payloads}
The consequences of exploiting an infiltrated origin depend on the capabilities 
of the format used. These consequences span from forging requests to the vulnerable website,
abusing the credentials of the victim, to extracting sensitive information about the user that is
stored on the vulnerable website.

@@

If the format has the capability of issuing requests, that includes the victims 
credentials, within the boundaries of the SOP, then this constitutes a 
\emph{cross-site request forgery} (CSRF) attack. Websites protect against these attacks by 
generating a token with each response that has to be included in the subsequent 
request. However, if the format also have the capability of reading the response 
the issued request, it can extract the token and thereby circumvent the CSRF 
protection.

@@

If the format also has the capability of communicating with the attacker, then 
the attacker can extract sensitive user information and leak it across origins. If the 
format is not restricted by the SOP, it can communicate directly with the 
attackers server. Otherwise, if the format can interact with the document that 
embeds the polyglot, the communication could be tunneled through this channel.

@@

%Much like a cross-site scripting attack, we consider a scenario where a
%website serves documents which are based upon user-supplied information.

@@

%The difference in this scenario from the previous one is in the nature of the
%vulnerability. Where in the previous scenario an existing document was injected
%to become a polyglot, this scenario targets services which allow an attacker to
%introduce new documents. As in the previous scenario, the target is a user of
%the vulnerable website.

@@

\subsection{PDF-based polyglots}
\label{sec:pdf-based-polyglots}
Several design choices in the PDF specification make the format particularly 
suitable for making polyglots. One such design choice is the error tolerant 
parser. This is in part motivated by PDF being a container format, 
%of which the 
another design choice which implies
%implication is 
that a PDF file can, by design, contain foreign syntax that 
could interfere with the syntax of the file. Another motivation is that PDF 
files are designed to be both forward- and backward-compatible. Readers 
implementing an older version of the specification do not recognize new 
features and behave as if they were not present in the file. 
%
The implementation notes of the specification describes some exceptions to the
requirements of the specification, such as the header can occur 
anywhere within the first 1024 bytes of the file. This flexibility gives plenty of room for 
combining with syntax of another format.
%
The specification declares many components to be required in a
PDF file, but as can be seen in Section~\ref{sec:format}, in practice several 
components can be omitted~\cite{Wolf:CCC10}. The code in Listing~\ref{lst:minimal-pdf} shows the 
minimal syntax required for a malformed, but valid PDF file.
%incrementally 
%updated by appending updated versions of existing objects to 
%the end of the file. In fact, 
%and formats. This and the fact that it is designed to be robust against errors,
%provides us with a format that is powerful, flexible and ideal for creating
%malicious polyglots.

@@

\subsubsection{Syntax injection}
\label{sec:pdf-injection}
As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
%
An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
%
The content is subsequently 
embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
requests to the origin it came from, carrying the cookies associated with that origin.
These requests allow for the extraction of sensitive user data that can either be 
communicated back to the attacker, or be leveraged in further attacks.

Thus far, exploitation of vulnerable services have been discussed, excluding the specific 
conditions under which a service is vulnerable. In order to exploit the 
vulnerability, the injected syntax must pass through any existing filters 
unchanged or at least with its semantics preserved. If user input in an 
HTML-document is not sanitized, any syntax would be unchanged and 
the service is vulnerable to less sophisticated attacks, e.g. cross-site scripting, 
therefore sanitized user input is of greater concern.
%
Based on the PDF samples in Listings~\ref{lst:minimal-pdf} and~\ref{lst:xml-pdf}, we can derive 
the set of tokens required to build a PDF. Assuming that alpha-numeric characters 
pass through a sanitization filter unmodified, the set of tokens is $\{\%, <<, >>, /\}$.
As can be noted, there is a small but significant overlap with the tokens of HTML, 
which implies that many websites protected against cross-site scripting attacks 
are also protected against PDF-based polyglot attacks. One of the problems of 
filtering input for inclusion in a web page are the many contexts in which the 
input can be included. A problem made even more complex by the diversity of 
languages the page contains. Language incompatibilities force context dependent 
filtering, where the same input is treated differently based on the context in 
which it is included. In certain contexts angle brackets are often left untouched by filters.

@@

\paragraph{JavaScript strings}
In an in-line JavaScript context, user input is often included in the shape of a 
JavaScript string, delimited by single or double quotes. In this context only a 
few characters require encoding, as they can break the string context. Naturally, 
any single or double quotes need escaping, as well as any carriage return or 
line feed characters. In the spirit of making minimal changes to the input, 
certain websites only escape these characters. This is sufficient to prevent cross-site 
scripting attacks, but fail to protect against PDF-based polyglot attacks.

Not only in-line JavaScript fall short in this regard. JavaScript object notation 
(JSON) is used in modern websites as a data transport. This is particularly 
common in websites that provide an API to interact with the offered services.
JSON encoded information suffer the same problem as in-line JavaScript, thereby
extending the attack surface further.

@@

%\paragraph{Fragment identifier}
%The methods that navigate the browser can still be used for a somewhat covert 
%communication with the attacker. Navigating to the same page with a different 
%fragment identifier will not reload the page. Embedding the information in the fragment 
%identifier of the URL of the embedding website, creates a one-way communication 
%channel from the document to the page. Since the fragment identifier is visible 
%in the address field of the browser, an alert user would notice it changing.

@@

This section details the evaluation performed to investigate the persistence of 
the vulnerabilities from Section~\ref{sec:vuln}. The evaluation covers various 
instances of affected components, such as browsers and PDF interpreters, 
content sanitization filter, and a study of the Alexa top 100 websites.

@@

The behavior of cross-domain embedding of PDF resources is studied in the major 
browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
The study shows that all major browsers are susceptible to the attacks outlined 
in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.
In Table~\ref{tab:comparison}, "Yes" for the columns "object" and "embed" indicates that the 
corresponding tag can be used to embed a PDF document, and for the column 
"Adobe is default" it indicates that Adobe Reader is the commonly default PDF reader.

@@

\paragraph{Content smuggling}
Further, a smaller study was conducted, not covering the full Alexa top 100, but 
targeting popular cloud storage services. 
This study is based on polyglot content being uploaded to the service and 
subsequently analyzed to determine which origin it was served
under. We have found two major 
enterprise cloud storage services to be susceptible to attacks. Both service makes an effort to
follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but fail to cover scenarios for content upload.

@@

As a content provider on the Internet today there are precautions that one can 
take to mitigate this class of vulnerabilities. Which precautions to take depend 
on the kind of services provided. The mitigation recommendations for syntax 
injection apply to all services that rely on user input, and the content smuggling
recommendations apply to services that serve user-supplied files.

@@

In the case of PDF-based polyglots, the browser can intervene when there is a 
mismatch between the content-type provided by the server and the type attribute 
of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there can be a potential security issue in 
interpreting the supplied content in the requested format and alerting the user to this
threat.

One may argue that the browser is as confused as the originating server as to the 
actual format of the content, and that the issue would be best resolved by the 
corresponding plug-in.

>>>>

\paragraph{Internet origins at stake}
The different trust domains
correspond to different Internet origins. A major goal for web
application security is preventing undesired communication across
origins. 
%
With the goal of separating information from the different origins,
today's browsers enforce the \emph{same-origin policy} (SOP). SOP
only allows access between two documents if they share the
origin. In addition, a document can only directly communicate with the
server from which it originates. 
%
%Typically a document is considered to be an HTML-page.

@@

\paragraph{Crossing origins by crossing formats}
This paper identifies a new breed of attacks and its root cause:
\emph{polyglots}. 
%
A polyglot is a program that is valid in multiple programming languages.
%
In a heterogeneous system like the web, information is exchanged
between components in versatile formats.
%
This gives rise to attacks that exploit the mismatch between the
expected and provided content.
%
Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
An attacker can use a polyglot to infiltrate a vulnerable origin.
Once infiltrated, the polyglot is embedded in the attackers web site using a plug-in.
According to the SOP, content loaded in a plug-in is considered to belong to the 
origin from which it was loaded, thus allowing the polyglot to communicate with the vulnerable 
origin. A victim visiting the attacker's web site, while authenticated in the vulnerable
origin, will activate the malicious polyglot, which can abuse the credentials of the victim 
in its communication with the vulnerable service. The scenario is explained in detail in Section~\ref{sec:vectors},
where we present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

\paragraph{Evaluation and mitigation}
We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web
sites.
%
Unfortunately, several major web sites do not protect against polyglot
attacks. Five out of the top 100 Alexa web sites are vulnerable to syntax injec
attacks. In addition,
we have found two major
enterprise cloud storage services to be susceptible to content
smuggling attacks.
%
Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (such as PDF readers) show how to mitigate the attacks.

@@

This section describes how formats can be crossed and how that can be abused 
to cross origins by circumventing the same-origin policy. We begin by 
describing cross-origin information leaks, next we
generalize the problem of crossing formats to \emph{polyglots} and describe the  
characteristics of a malicious polyglot. From that we derive two attack vectors and 
show how previous work on the subject relate to these vectors.

@@

Another example of problematic elements include the \emph{object} and
\emph{embed} tags. These 
tags allow inclusion of resources that may require a 
plug-in to run. The plug-in is selected based on the MIME-type of the content, but
because the server delivering the content might not be able to determine its
format, the tags allow a developer to set the type attribute to guide the
browser in which plug-in to run. When the type attribute is used, the
corresponding plug-in is run regardless of the MIME-type provided by the server. 
%
In the event that the provided MIME-type do not match that for which the plug-in is 
designed, e.g., \emph{text/html} for a PDF plug-in, it is up to the plug-in to respond to the content it is served.
Known methods of handling MIME-types, such as content-sniffing, are effective 
in this situation, but they have to be employed by each and every plug-in.
Most plug-ins will disregard the MIME-type of the content and attempt to parse 
it. 
%
As with images, the content handled by the plug-in is executed in the origin it was served from. 
This implies that the containing page is restricted 
from directly accessing the content handled by the plug-in, and that the content can 
communicate freely with the origin it was loaded from. However,  a number of plug-ins provide 
an API for interaction between the plug-in and the document.
The browsers are forced to rely on the plug-ins to employ correct security 
measures. Section~\ref{sec:eval} shows that even state-of-the-art plug-ins fail to 
properly do so, emphasizing the importance of increasing awareness on the issue. 
%Next we show how crossing formats
%to cross-origin information leaks.

@@

Barth et al.~\cite{Barth+:SP09} define \emph{chameleon} documents 
as a benign file type crossbred with malicious HTML content. The attack 
targets the content-sniffing algorithm used in the browser and the document 
is crafted in such a way that the browser 
will detect the content type as HTML. The paper proceeds to 
describe how an attacker can create a 
\emph{chameleon} document, that is valid PostScript, but will be identified as HTML.
This issue allows exploitation when there is a mismatch between a web site's 
content validation filter and the browsers content-sniffing algorithm.

In literature we find, apart from chameleons, other names for similar,
related concepts. Brandis~\cite{Brandis:GIFAR} refer to \emph{GIFAR} 
attacks, based on one of the early instances of attacks based on 
GIF images that are also valid JAR files. 
Sundareswaran et al.~\cite{Sundareswaran:Squicciarini:CEAS10,Sundareswaran:Squicciarini:SecureComm10}
discuss GIFAR-related attacks as a form of \emph{content repurposing} attack. 
In this paper the term content smuggling is used as it best represents 
how a polyglot can infiltrate an origin.

@@

\subsection{Attack vectors}
\label{sec:vectors}
%In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more %than one way.

The general pattern of a polyglot attack is described in the following scenario, illustrated in Figure~\ref{fig:scenario}. 
The target of the attack is the web site \emph{vulnerable.com}. It has been 
infiltrated by an attacker to serve a malicious polyglot within its sensitive origin (1).
The content is served by \emph{vulnerable.com} as the benign format, e.g., an image, harmless 
to users of the web site.
The victim in this scenario is an authenticated user of \emph{vulnerable.com}.
At some point, while still authenticated to \emph{vulnerable.com}, 
the unsuspecting victim visits the attackers web site \emph{attacker.com} (2).
Upon visiting \emph{attacker.com}, the web site uses a plug-in to embed the 
polyglot from \emph{vulnerable.com} as the malicious format (3). This is achieved by 
setting the type attribute to the MIME-type of the corresponding plug-in, which 
will override the MIME-type supplied by \emph{vulnerable.com}. When loaded in 
the plug-in the malicious polyglot is executed in the \emph{vulnerable.com} origin (4), 
as described in Section~\ref{sec:cross-origin}. The impact depends on the 
payload and the capabilities of the malicious format.

This paper identifies two vectors for infiltrating an origin, either via syntax 
injection, or content smuggling. In the case of syntax injection, existing content is manipulated
to become a polyglot, whereas with content smuggling, a polyglot is used to evade 
content filters. The vectors are described below with more detailed scenarios.

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{scenario.png}
  \caption{Overview of the scenario}
  \label{fig:scenario}
\end{figure}

\subsubsection{Syntax injection}
\label{sec:injection}
In a cross-site scripting attack user input is used to compose an HTML document. 
Fragments of HTML-syntax in the input alters the semantic of the document to 
execute attacker supplied 
script code. Similarly, in a syntax injection attack the vulnerable target will 
compose an HTML document from attacker controlled input containing syntax of a foreign 
format. The resulting document is a polyglot which is benign when viewed as the 
HTML, but malicious when viewed as the injected format. While the 
web site serves the content as HTML, it is in the hands 
of the attacker to decide how it is interpreted when embedded in the attackers web page. Examples of 
such services include social networks, search engines, i.e., nearly any dynamic web site driven by user interaction.
%
The targeted service is assumed to employ server-side cross-site scripting 
sanitization. For the attack to be successful, the input must 
bypass this sanitization. The sanitization filter will remove or encode 
problematic characters in the input related to HTML-syntax. The injected format will 
pose as a new context, unknown to the filter. Chances are that the 
injected format will pass the filter unnoticed.

@@

\paragraph{Scenario}
The scenario, illustrated in Figure~\ref{fig:injection-scenario}, describes how 
the attack proceeds from the infiltration of the origin to the compromise of the victim.
Again, the victim is an authenticated user of \emph{vulnerable.com} that 
unsuspectingly visits the attackers malicious web site, \emph{attacker.com} (1). 
The \emph{attacker.com} web site uses a plug-in to embed a web page with 
vulnerable input parameters from \emph{vulnerable.com} (2). 
In the parameters of the request the attacker injects the syntax of the malicious format (3).
The response from \emph{vulnerable.com} is a polyglot served as the benign content type (4), but
the attacker's page coerces the content to be interpreted as the malicious content type by the plug-in.
The malicious payload is executed in the origin of \emph{vulnerable.com} and can 
leverage the credentials of the victim to further exploit the vulnerability.

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{injection-scenario.png}
  \caption{Syntax injection scenario}
  \label{fig:injection-scenario}
\end{figure}

@@

\subsubsection{Content smuggling}
\label{sec:smuggling}
The vulnerable target of a content smuggling attack, lets 
users upload files that are subsequently served under the origin of 
the service. Examples of such potentially vulnerable services are cloud storage services, image databases, 
social networks, conference management systems or job broker services. Such a service 
accepts a limited set of benign file-formats, and the files are run through a filter to verify that they 
belong to this set, e.g. images or documents, before being served to the end
user. The
filter will verify the file under the assumption that it conforms strictly to one format. 
By submitting a polyglot to such a service, an attacker can evade the filter as the polyglot does conform to the benign format.
If the polyglot is publicly accessible, it can be embedded in the attackers 
page. Since the attacker is in control over which format the polyglot is 
interpreted as, it is embedded as the malicious format and thereby the 
service is vulnerable to a content smuggling attack.

@@

\paragraph{Scenario}
The content smuggling scenario proceeds as illustrated in Figure~\ref{fig:smuggling-scenario}.
Similarly to the previous scenarios, the victim is an authenticated user of a targeted vulnerable web site, \emph{vulnerable.com}. 
To give more context to the scenario, \emph{vulnerable.com} can be a cloud storage service. 
The target is infiltrated by the attacker (1), who uploads a polyglot to the web site. 
The polyglot is verified to be benign under the assumption that it belongs an allowed file type.
%The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
While still authenticated to \emph{vulnerable.com}, 
the victim visits the attackers web site, \emph{attacker.com} (2).
The \emph{attacker.com} site embeds the polyglot from \emph{vulnerable.com} (3), which is served as the benign type, but 
coerced to be interpreted as the malicious content type by the plug-in (4). 
The malicious format of the embedded 
polyglot is activated and a possible payload is to extract all the files stored in the victims account.

@@

\begin{figure}[t]
  \center
  \includegraphics[width=0.49\textwidth]{smuggling-scenario.png}
  \caption{Content smuggling scenario}
  \label{fig:smuggling-scenario}
\end{figure}

\subsection{Payloads}
\label{sec:payloads}
The consequences of exploiting an infiltrated origin depend on the capabilities 
of the format used. These consequences span from abusing the credentials of 
the victim to forge requests to the vulnerable web site, to extracting sensitive 
information about the victim that is stored on the vulnerable web site.

@@

If the format has the capability of issuing requests, in particular POST requests
within the boundaries of the SOP, that includes the victims 
credentials,then the attacker can mount a  
\emph{cross-site request forgery} (CSRF) attack. Web sites protect against these attacks by 
generating a token with each response that has to be included in the subsequent 
request. However, if the format also have the capability of reading the response of 
the issued request, it can extract the token and thereby circumvent the CSRF 
protection.

@@

Additionally, if the format allows communication with the origin of the attacker, then 
the attacker can extract sensitive user information and leak it across origins. If the 
format is not restricted by the SOP, it can communicate directly with the 
attackers server. Otherwise, if the format can interact with the document that 
embeds the polyglot, the communication could be tunneled through this channel.

@@

%Much like a cross-site scripting attack, we consider a scenario where a
%web site serves documents which are based upon user-supplied information.

@@

%The difference in this scenario from the previous one is in the nature of the
%vulnerability. Where in the previous scenario an existing document was injected
%to become a polyglot, this scenario targets services which allow an attacker to
%introduce new documents. As in the previous scenario, the target is a user of
%the vulnerable web site.

@@

\subsection{PDF-based polyglots}
\label{sec:pdf-based-polyglots}
Several design choices in the PDF specification make the format particularly 
suitable for making polyglots. One such design choice is the error tolerant 
parser. This is in part motivated by another design choice namely PDF being a container format. 
%of which the 
This implies
%implication is 
that a PDF file can, by design, contain foreign syntax that 
could interfere with the syntax of the file. Another motivation is that PDF 
files are designed to be both forward- and backward-compatible. Readers 
implementing an older version of the specification do not recognize new 
features and behave as if they were not present in the file. 
%
The implementation notes of the specification describes some exceptions to the
requirements of the specification, such as the header can occur 
anywhere within the first 1024 bytes of the file. This flexibility gives plenty of room for 
combining with syntax of another format.
%
The specification declares many components to be required in a
PDF file, but as can be seen in Section~\ref{sec:format}, in practice several 
components can be omitted~\cite{Wolf:CCC10}. The code in Listing~\ref{lst:minimal-pdf} shows the 
minimal syntax required for a malformed, but valid PDF file.
%incrementally 
%updated by appending updated versions of existing objects to 
%the end of the file. In fact, 
%and formats. This and the fact that it is designed to be robust against errors,
%provides us with a format that is powerful, flexible and ideal for creating
%malicious polyglots.

@@

\subsubsection{Syntax injection}
\label{sec:pdf-injection}
As the scenario details in Section~\ref{sec:injection}, the attacker in a syntax 
injection attack manipulates a vulnerable service to include PDF syntax in existing content, e.g. HTML-documents.
The PDF syntax is typically injected through user input used by the vulnerable service in the composition of documents.
%
An example of a suitable fragment to inject is shown in Listing~\ref{lst:xml-pdf}.
%
The resulting content is subsequently 
embedded in the attackers page as PDF, as exemplified in Listing~\ref{lst:embed-pdf}.
As mentioned in Section~\ref{sec:pdf-based-polyglots}, the embedded PDF can issue 
requests to the origin it came from, carrying the cookies associated with that origin.
These requests allow for the extraction of sensitive user data that can either be 
communicated back to the attacker, or be leveraged in further attacks.

Thus far, exploitation of vulnerable services have been discussed, excluding the specific 
conditions under which a service is vulnerable. In order to exploit the 
vulnerability, the injected syntax must pass through any existing filters 
unchanged or at least with its semantics preserved. If user input in an 
HTML-document is not sanitized, any syntax would be unchanged and 
the service is vulnerable to less sophisticated attacks, e.g. cross-site scripting, 
therefore sanitized user input is of greater concern.
%
Based on the PDF samples in Listings~\ref{lst:minimal-pdf} and~\ref{lst:xml-pdf}, we can derive 
the set of tokens required to build a PDF. Assuming that alpha-numeric characters 
pass through a sanitization filter unmodified, the set of tokens is $\{\%, <<, >>, /\}$.
As can be noted, there is a small but significant overlap with the tokens of HTML, 
which implies that many web sites protected against cross-site scripting attacks 
are also protected against PDF-based polyglot attacks. One of the problems of 
filtering input for inclusion in a web page are the many contexts in which the 
input can be included. A problem made even more complex by the diversity of 
languages the page contains. Language incompatibilities force context dependent 
filtering, where the same input is treated differently based on the context in 
which it is included. In certain contexts angle brackets are often left untouched by filters.

@@

\paragraph{JavaScript strings}
In an in-line JavaScript context, user input is often included in the shape of a 
JavaScript string, delimited by single or double quotes. In this context only a 
few characters require encoding, as they can break the string context. Naturally, 
any single or double quotes need escaping, as well as any carriage return or 
line feed characters. In the spirit of making minimal changes to the input, 
certain web sites only escape these characters. This is sufficient to prevent cross-site 
scripting attacks, but fail to protect against PDF-based polyglot attacks.

Not only in-line JavaScript fall short in this regard. JavaScript object notation 
(JSON) is used in modern web sites as a data transport. This is particularly 
common in web sites that provide an API to interact with the offered services.
JSON encoded information suffer the same problem as in-line JavaScript, thereby
extending the attack surface further.

@@

%\paragraph{Fragment identifier}
%The methods that navigate the browser can still be used for a somewhat covert 
%communication with the attacker. Navigating to the same page with a different 
%fragment identifier will not reload the page. Embedding the information in the fragment 
%identifier of the URL of the embedding web site, creates a one-way communication 
%channel from the document to the page. Since the fragment identifier is visible 
%in the address field of the browser, an alert user would notice it changing.

@@

This section details the evaluation performed to investigate the persistence of 
the vulnerabilities from Section~\ref{sec:vuln}. The evaluation covers various 
instances of affected components, such as browsers and PDF interpreters, 
content sanitization filter, and a study of the Alexa top 100 web sites.

@@

The behavior of cross-domain embedding of PDF resources is studied in the major 
browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
The study shows that all major browsers are susceptible to the attacks outlined 
in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.
In Table~\ref{tab:comparison}, "Yes" for the columns "object" and "embed" indicates that the 
corresponding tag can be used to embed a PDF document, and for the column 
"Adobe is default" it indicates that Adobe Reader is commonly the default PDF reader.

@@

\paragraph{Content smuggling}
Further, a smaller study was conducted, not covering the full Alexa top 100, but 
targeting popular cloud storage services. 
This study is based on polyglot content being uploaded to the service and 
subsequently analyzed to determine which origin it was served 
under. We have found two major 
enterprise cloud storage services to be susceptible to attacks. Both services make an effort to
follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but 
fail to cover scenarios for content upload.

@@

As a content provider on the Internet today there are precautions that one can 
take to mitigate this class of vulnerabilities. Which precautions to take depend 
on the kind of services provided. The mitigation recommendations for syntax 
injection apply to all services that generate content based on user input, and the content smuggling
recommendations apply to services that serve user-supplied files.

@@

In the case of PDF-based polyglots, the browser can intervene when there is a 
mismatch between the content-type provided by the server and the type attribute 
of the \emph{object} tag. The vulnerability can be mitigated by acknowledging that there is a potential security issue in 
interpreting the supplied content in the requested format and alerting the user to this
threat.

An intuitive approach would be to for the browsers to employ similar content-sniffing
for content rendered in plug-ins, as is already done with content native to the browser.
However, this intuition fails to take into account that the very reason for using plug-ins 
is that the format is unknown to the browser. 
One may argue that the browser is as confused as the originating server as to the 
actual format of the content, and that the issue would be best resolved by the 
corresponding plug-in.
